---
title: "Classwork 10"
editor: visual
author: Jaxson Marsh

toc: true
toc-title: "Table of Contents"
toc-depth: 2
number-sections: true

fig-width: 9

execute:
  code-tools: true
  message: false
  warning: false

from: markdown+emoji
---

```{r setup}
#| include: false
library(tidyverse)
library(skimr)
library(dplyr)
library(ggthemes)
library(hrbrthemes)

theme_set(theme_ipsum()+
          theme(strip.background =element_rect(fill="lightgray"),
                axis.title.x = 
                  element_text(angle = 0,
                               size = rel(1.33),
                               margin = margin(10,0,0,0)),
                axis.title.y = 
                  element_text(angle = 0,
                               size = rel(1.33),
                               margin = margin(0,10,0,0))
                )
          )
```

# Billboard Charts

The following data is for Question 1:

```{r}
billboard <- read_csv('https://bcdanl.github.io/data/billboard.csv')
```
```{r}
#| results: asis
#| echo: false
rmarkdown::paged_table(billboard) 
```


### 1a

Describe how the distribution of rating varies across week 1, week 2, and week 3 using the faceted histogram.

```{r}

```


### 1b

- Which artist(s) have the most number of tracks in billboard data.frame?

- Do not double-count an artist’s tracks if they appear in multiple weeks.

```{r}
artist_track_counts <- billboard %>%
  group_by(artist) %>%
  summarise(unique_tracks = n_distinct(track))

top_artists <- artist_track_counts %>%
  filter(unique_tracks == max(unique_tracks))
```




# Average Personal Income in NY Counties

The following data is for Question 2:

```{r}
ny_pincp <- read_csv('https://bcdanl.github.io/data/NY_pinc_wide.csv')
```

```{r}
#| results: asis
#| echo: false
rmarkdown::paged_table(ny_pincp) 
```


### 2a

Make ny_pincp longer.

```{r}
q2a <- ny_pincp %>% 
  pivot_longer(cols = pincp1969:pincp2019,
               names_to = "year",
               values_to = "pincp")
```


### 2b

```{r}

```






