---
title: "Classwork 10"
editor: visual
author: Jaxson Marsh
affiliations: SUNY Geneseo
---

```{r}
#| include: false
library(tidyverse)
library(skimr)
library(dplyr)
library(ggthemes)
library(hrbrthemes)
```

### Question 1 - Billboard Charts

The following data is for Question 1:

```{r}
billboard <- read_csv('https://bcdanl.github.io/data/billboard.csv')
```
```{r}
#| results: asis
#| echo: false
rmarkdown::paged_table(billboard) 
```


## Q1a

Describe how the distribution of rating varies across week 1, week 2, and week 3 using the faceted histogram.

```{r}

```


## Q1b

- Which artist(s) have the most number of tracks in billboard data.frame?

- Do not double-count an artist’s tracks if they appear in multiple weeks.

```{r}
artist_track_counts <- billboard %>%
  group_by(artist) %>%
  summarise(unique_tracks = n_distinct(track))

top_artists <- artist_track_counts %>%
  filter(unique_tracks == max(unique_tracks))
```




### Question 2 - Average Personal Income in NY Counties

The following data is for Question 2:

```{r}
ny_pincp <- read_csv('https://bcdanl.github.io/data/NY_pinc_wide.csv')
```

```{r}
#| results: asis
#| echo: false
rmarkdown::paged_table(ny_pincp) 
```


## Q2a

Make ny_pincp longer.

```{r}
q2a <- ny_pincp %>% 
  pivot_longer(cols = pincp1969:pincp2019,
               names_to = "year",
               values_to = "pincp")
```


## Q2b







