---
title: DANL Project
subtitle: "Data-Driven Mastery: Unlocking Business Potential"
author: 
  - Jaxson Marsh
  - Edward Eforo
  - Angelina Batista
  - Daniel Noone
  - Elizabeth Dutan

toc: true
toc-title: "Table of Contents"
toc-depth: 2
number-sections: true

fig-width: 9

execute:
  code-tools: true
  message: false
  warning: false

from: markdown+emoji
---
```{r setup}
#| include: false
library(tidyverse)
library(skimr)
library(ggthemes)
library(hrbrthemes)

theme_set(theme_ipsum()+
          theme(strip.background =element_rect(fill="lightgray"),
                axis.title.x = 
                  element_text(angle = 0,
                               size = rel(1.33),
                               margin = margin(10,0,0,0)),
                axis.title.y = 
                  element_text(angle = 0,
                               size = rel(1.33),
                               margin = margin(0,10,0,0))
                )
          )
```



# Introduction

The following dataframe was used for this project :sleeping:

```{r}
sleephealth <- read.csv("C:/Users/Jaxso/Downloads/Sleep_health_and_lifestyle_dataset.csv")
```


# Data

The data.frame `sleephealth` contains a subset of the fuel economy data that the EPA makes available on [https://kaggle.com/](https://fueleconomy.gov/). It comprises 400 rows and 13 columns, covering a wide range of variables related to sleep and daily habits. It includes details such as gender, age, occupation, sleep duration, quality of sleep, physical activity level, stress levels, BMI category, blood pressure, heart rate, daily steps, and the presence or absence of sleep disorders. :bed:


## Summary Statistics

```{r}
mpg <- ggplot2::mpg
```

```{r}
#| results: asis
#| echo: false
rmarkdown::paged_table(sleephealth) 
```


```{r}
skim(sleephealth) %>% 
  select(-n_missing)
```

## Quality of Sleep Under Stress
The following boxplot shows how the distribution of Quality of Sleep (`Quality.of.Sleep`) varies by a Stress Level (`Stress.Level`) :sleeping: :bed: :angry:.


```{r}

```


